---
title: "ArrivalDistWoman"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
 

```

we will need the following libraries: fitdistrplus, magrittr
```{r libraries, include=TRUE,echo=TRUE}
library(fitdistrplus)
library(magrittr)
```

Now our samples will probably not include any negative values. We also got alot more samples. 
```{r}
table <- read.csv(file.choose(),header = T)
Samples <- table[,6]

```

first impression

```{r empirical plots2}
par(mfrow=c(1,3)) # defines 2 plots on the same window
plot(Samples,ylab="Sample values") # plot ( left graph )
hist(Samples, ylab="Frequency ") # histogram (right graph)
boxplot(Samples)
```

We will try again the normal fit and exp fit:

```{r}
normFit<-fitdist(Samples,"norm") # fitting a normal distrbution 
summary(normFit) # summary function displays the results 
expFit<-fitdist(Samples,"exp") # now the fit will work 
summary(expFit)
```

We can see the difference in the Loglikelihood and in the BIC/AIC. We want higher Loglikelihood, and lower AIC/BIC.

**We can conclude that the normal distribution fits our data better** 
** Note that in real cases you dont know where the samples came from, and you should try different distributions that might fit and compare using Loglikelihood or BIC** 
This will be seen from the plots as well:
```{r}
plotdist(Samples,"norm",para=list(mean=normFit$estimate[1], sd=normFit$estimate[2] ) )
plotdist(Samples,"exp",para=list(rate=expFit$estimate[1]))

```



** The graphs can be combined into one graph in the following manner: ** 

```{r}
par(mfrow=c(2,2)) # manually define a 2X2 graph window 
legendText<-c("exp","norm") # define legend text
denscomp(list(expFit,normFit),legendtext=legendText) # histograms
qqcomp(list(expFit,normFit),legendtext=legendText)  # qq plot
cdfcomp(list(expFit,normFit),legendtext=legendText) # cdf plot
ppcomp(list(expFit,normFit),legendtext=legendText) # pp plot
```


## 4. Perform Goodness of Fit tests on fitted distribution

Now that we found a fitting distribution, we need to statisticlly test the hypothesis our data came from this distribution. for that we can use Goodness of Fit tests (GOF). We can choose between Chi-Squared (CHISQ) or Kolmogorov-Smirnov (KS).
We will use the general function gofstat:

```{r}
normgof<- gofstat(normFit)%>%print()
normgof$kstest%>%print()
```

The default test for continous distributions will be KS. 
The normal distribution test - H0 is not denied, and hence we can conclude the data came from this normal distribution. 

If we want to perform Chi-squared test for continuous distribution it can be forced using the "discrete = TRUE" parameter:

```{r}
normgof<- gofstat(normFit, discrete=TRUE)%>%print()

```

```{r}
expgof<- gofstat(expFit)%>%print() 
expgof$kstest%>%print()
```
For exp Fit - H0 is denied. 

